\subsubsection{Dataset}

\begin{itemize}
    \item \textbf{FR-1.-} The application should allow the use of the Wisconsin breast cancer dataset or one with the same features.
    \item \textbf{FR-2.-} The dataset should be split into a training and testing dataset using a 70-30 ratio.
\end{itemize}

\subsubsection{Classifiers}

\begin{itemize}
    \item \textbf{FR-3.-} The application should employ the features provided in the dataset for classifier comparison and XAI.
    \item \textbf{FR-4.-} The application should work with multiple classifiers for breast cancer detection.
    \item \textbf{FR-5.-} The application should preprocess the dataset before feeding it to the classifiers. This may include steps such as normalization, and feature selection, focusing on reproducibility and repeatability.
    \item \textbf{FR-6.-} The application should use a test dataset for classifier comparison.
    \item \textbf{FR-7.-} The application should use evaluation metrics to determine the effectiveness of the classifiers taking into account the nature of the problem.
\end{itemize}

\subsubsection{Explainable Artificial Intelligence}

\begin{itemize}
    \item \textbf{FR-8.-} The application should show which features are the most important for a classifier.
    \item \textbf{FR-9.-} The application should show how sure the classifier was of its prediction.
    \item \textbf{FR-10.-} The application should show which features determined if the sample was benign or malignant.
\end{itemize}

\subsubsection{Web Application}

\begin{itemize}
    \item \textbf{FR-11.-} The web application should have a home page with a slideshow with information.
    \item \textbf{FR-12.-} The web application should display a list with all the classifiers.
    \item \textbf{FR-13.-} The web application should show a details page about each classifier, showing its metrics, most important features, and examples of decisions made by the classifier.
    \item \textbf{FR-14.-} The web application should compare any two classifiers showing their metrics and most important features.
\end{itemize}
