Throughout the writing of this thesis, some limitations and future work have been identified. We would like to propose the following ideas for future research:

\textbf{Use the FNAB image instead of parametrized version:} The dataset used in this thesis contains parametrized images of breast cancer \ac{fnab} samples, that is, the images are represented as a set of numerical values. In future research, it would be interesting to use the actual images of the samples to train the model. This would increase the ease of use of the model in a real-world scenario, as it would be able to classify the samples directly from the images without the need for additional processing.

\textbf{Bigger dataset:} The dataset used in this thesis contains 569 samples, which is relatively small for a machine-learning model. In future research, it would be interesting to use a larger dataset to train the model. This would allow the model to learn more complex patterns and improve its performance, even though it may require more time and resources to evaluate the models as exhaustively as we did here.

\textbf{Try this with a doctor:} In future research, it would be interesting to test the model with a doctor to evaluate not only its numerical performance (which is important but can be done without a doctor) but to evaluate how the model can help a doctor in their diagnostic process. This would provide valuable insights into the model's real-world applicability and its potential impact on the healthcare sector.

\textbf{Test with other classifier models:} In this thesis, we tested different classifier models and selected the best one based on a set of metrics. In future research, it would be interesting to test other classifier models to see if they can outperform the selected model. 

\textbf{Use other \ac{xai} techniques:} We used \ac{shap} library to provide explanations for the model's predictions. In future research, it would be interesting to use other \ac{xai} techniques to provide explanations for the model's predictions.

\textbf{Generalize the model for other cancer types:} We focused on classifying breast cancer \ac{fnab} samples as benign or malignant. In future research, it would be interesting to generalize the model to classify other types of cancers, or even other types of examinations which are not biopsies.